How did the introduction of Stemmed Points affect Mobility and Site Occupation during the Late Pleistocene in Korea?

### 2021-04-12 analysis/paper/paper.Rmd
resolve merge conflict

```{r climate-model, fig.cap="Mean Annual Temperature (MAT) of the Korean Paleolithic assemblages mentioned in the text. A: Site locations and their MAT. B: MAT distributions for each site during the period they were occupied. C: MAT from 50 ka to 10 ka. The grey lines indicate the MAT for each site and the black line is the mean temperature of all sites. The light grey area in the middle of the plot indicates the duration of MIS 2, and the dark grey area represents the duration of the  LGM. D: The relationship between MAT and site elevation. The blue line is a linear regression on elevation and MAT with the grey area showing the 95% confidence interval.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/007-climate-model-plots.R"))}
quietly(source(here::here("analysis/paper/007-climate-model-plots.R")))
knitr::include_graphics(here::here("analysis/figures/007-climate-model-sites-panel-plot.png"))
```

@@

```{r spd-model, fig.cap="Summed probability distribution of 108 radiocarbon dates. The black solid line represents actual radiocarbon ages. The grey shaded region shows the Monte Carlo envelope that encompasses the 95% confidence interval for the null models. The red and blue vertical bands highlight the portions of the SPD where positive and negative deviations are detected. We applied logistic, exponential and linear to AIC along with the logistical growth model (fit) to evaluate each model [@riris2019widespread]. We excluded the uniform model because it has no fitted curve or surface to evaluate. The best fit model has the lowest AIC score. In this case, the linear model is the best fit for the observed data", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/008-summed-probability-distributions.R"))}
quietly(source(here::here("analysis/paper/008-summed-probability-distributions.R")))
knitr::include_graphics(here::here("analysis/figures/008-summed-probability-distribution-models.png"))
```

>>>>

```{r climate-model, fig.cap="Mean Annual Temperature (MAT) of the Korean Paleolithic assemblages mentioned in the text. A: Site locations and their MAT. B: MAT distributions for each site during the period they were occupied. C: MAT from 50 ka to 10 ka. The grey lines indicate the MAT for each site and the black line is the mean temperature of all sites. The light grey area in the middle of the plot indicates the duration of MIS 2, and the dark grey area represents the duration of the  LGM. D: The relationship between MAT and site elevation. The blue line is a linear regression on elevation and MAT with the grey area showing the 95% confidence interval.", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/007-climate-model-plots.R"))}
# quietly(source(here::here("analysis/paper/007-climate-model-plots.R")))
knitr::include_graphics(here::here("analysis/figures/007-climate-model-sites-panel-plot.png"))
```

@@

```{r spd-model, fig.cap="Summed probability distribution of 108 radiocarbon dates. The black solid line represents actual radiocarbon ages. The grey shaded region shows the Monte Carlo envelope that encompasses the 95% confidence interval for the null models. The red and blue vertical bands highlight the portions of the SPD where positive and negative deviations are detected. We applied logistic, exponential and linear to AIC along with the logistical growth model (fit) to evaluate each model [@riris2019widespread]. We excluded the uniform model because it has no fitted curve or surface to evaluate. The best fit model has the lowest AIC score. In this case, the linear model is the best fit for the observed data", cache=TRUE, cache.extra=tools::md5sum(here::here("analysis/paper/008-summed-probability-distributions.R"))}
# quietly(source(here::here("analysis/paper/008-summed-probability-distributions.R")))
knitr::include_graphics(here::here("analysis/figures/008-summed-probability-distribution-models.png"))
```
